%-------------------------
% Resume in Latex
% Author : Pranav Shukla
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\usepackage[sfdefault]{plex-sans}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Pranav Shukla} \\ \vspace{1pt}
    \small +1(248)-403-0495 $|$ \href{mailto:pranavshuklajobs@gmail.com}{\underline{pranavshuklajobs@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/pranavshhh/}{\underline{linkedin.com/in/pranavshhh/}} $|$
    \href{https://github.com/FireTeamSix}{\underline{github.com/FireTeamSix}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Michigan State University}{East Lansing, MI}
      {Bachelor of Science in Computer Science}{Sep. 2020 -- May 2024}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Computer Languages}{: Python, C++, JavaScript, HTML/CSS, SQL} \\
     \textbf{Technologies}{: AWS, React, Django, PostgreSQL, Docker, Kubernetes, Tensorflow, Pandas, UNIX, Atlassian Suite} \\
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineering Intern}{May 2022 -- Aug. 2022}
      {The Vanguard Group}{Malvern, PA}
      \resumeItemListStart
        \resumeItem{Assisted with development of Vanguard's cloud infrastructure to connect to new stock data providers, saving nearly \$600,000 per month in AWS costs.}
        \resumeItem{Created an AWS Lambda hosted Function-as-a-Service (FaaS) which uses Python's boto3 library to crawl through and delete data from Vanguard AWS Glue databases.}
        \resumeItem{Wrote unit tests with pytest to achieve 100\% test coverage, proving reliability of Lambda function.}
        \resumeItem{Configured 10 Atlassian Bamboo builds using YAML, directing storage manipulation services to the proper AWS servers.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
    \resumeSubheading
        {Business Analyst Intern}{May 2020 -- Aug. 2020}
        {Chime Menu, RecTable LLC.}{Ann Arbor, MI}
        \resumeItemListStart
            \resumeItem{Decreased onboarding time up to 50\% by developing strategy to onboard customers to RecTable's ordering system.}
            \resumeItem{Developed onboarding policies for client mastery of software and effortless implementation into existing POS systems.}
            \resumeItem{Increased customer numbers 75\% by presenting competitive analysis decks to chief officers and changing product strategy.}
    \resumeItemListEnd


    \resumeSubheading
      {Research Assistant}{Sep. 2021 -- Mar. 2022}
      {Intelligent Data Analytics (ILLIDAN) Lab}{East Lansing, MI}
      \resumeItemListStart
        \resumeItem{Reviewed and presented my knowledge from 3 deep learning research papers to the Lead
        Researcher and several other PhD candidates.}
        \resumeItem{Worked with researchers to integrate long short-term memory modules with Python deep learning algorithms, and applying it to Spatial Neural Networks that analyze limit order books.}
    \resumeItemListEnd

    \resumeSubheading
      {Technician}{Nov. 2021 -- Present}
      {Michigan State University ComArtSci}{East Lansing, MI}
      \resumeItemListStart
        \resumeItem{Ran technical operations and helped over 350 staff and students with problems arising
        from software and hardware.}
        \resumeItem{Engaged with MSU Staff to ensure network outages were fixed quickly, and servers were kept
        running.}
        \resumeItem{Reimaged both Macintosh and Windows computers to conform to MSU IT Security standards.}
        \resumeItem{Set up WiFi wiring throughout ComArtSci building, giving more than 3,500 people
        secure access to the internet.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AirFleet} $|$ \emph{Python, Django, JavaScript, React, PostgreSQL, AWS, aviationstack API}}{July 2021 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a Pilot’s Logbook web app that allows users to log-in and add entries to their logbooks, including features such as adding photos and route-waypoint storage.}
            \resumeItem{Created and connected a PostgreSQL database that stores all data, and is maintained on AWS Lightsail.}
            \resumeItem{Implemented RESTful architecture with Django for entry, updating, and deletion of logbook data by users, and connected it to a frontend using React to give a smooth user experience.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Stock Correlator} $|$ \emph{Python, BeautifulSoup4, SciKit-Learn, Yahoo! Stocks API, pandas}}{May 2020 -- June 2021}
          \resumeItemListStart
            \resumeItem{Scraped S\&P 500 stock tickers on Wikipedia using Python's BeautifulSoup4 library, and used Yahoo! Stocks API to pull all OHLC data since 2000 into a pandas dataframe.}
            \resumeItem{Using SciKit-Learn, algorithmically calculated R2 value of Adjusted Closes between ~500
            companies, which is displayed on to a 500 x 500 matplotlib heatmap, including color-coding for
            positive and negative correlations.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%



%-------------------------------------------
\end{document}
